\LARGE \bf Informed sampling by Markov Chain Monte Carlo methods

### 2017-01-26 paper.tex
?

\makeatletter
\let\NAT@parse\undefined
\makeatother

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sec:intro}

Sampling-based motion-planning algorithms~\cite{CBHKKLT05, L06} have proven to be an effective tool at solving motion-planning problems.
They search through the continuous state space~$\calX$ by sampling random states and maintaining a discrete graph~$G$ called a \emph{roadmap}.
Vertices and edges in $G$ correspond to collision-free states and paths, respectively.

@@

@@

\section{Related work}
\label{sec:related_work}

@@

Markov Chain Monte Carlo(MCMC)~\cite{ADDJ03} is a framework of sampling from a given probability distribution by constructing a Markov chain of random transition toward a desired distribution.
A set of samples are generated to approximate the desired distribution.
Unlike a rejection sampling, MCMC does a random walk in a parametric space and concentrates on an important areas, which usually brings better efficiency.
Hamiltonian Monte Carlo(HMC)~\cite{N11} is introduced to provide better efficiency in converging to a desired distribution.
It adopts physical system dynamics to propose future states in the Markov chain.

\section{Algorithm}
\label{sec:algorithm}

\begin{algorithm}
	\begin{algorithmic}[1]
		\STATE
   	\end{algorithmic}
	\caption{MCMC Informed Sampling}
	\label{alg:mcmc_informed_sampling}
\end{algorithm}

>>>>

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
Sampling-based motion-planning algorithms~\cite{CBHKKLT05, L06} have proven to be an effective tool at solving motion-planning problems.
They search through the continuous state space~$\calX$ by sampling random states and maintaining a discrete graph~$G$ called a \emph{roadmap}.
Vertices and edges in $G$ correspond to collision-free states and paths, respectively.

@@

In this paper, we suggest an alternative approach to sampling in the informed set \Cinf.
We call our approach

@@

\section{Related work}

@@

MCMC~\cite{ADDJ03}

HMC~\cite{N11}

\section{Algorithm}
